systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2004-11-16 paper/trunk/systemfit.tex
added cvs header and log section. to be removed when submitted.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@564 591db2bd-e0a0-4d22-8c19-2192dbb7da31

@@

\code{
R> library( systemfit ) \\
R> data( ppine ) \\
R> hg.formula <- hg $\sim$ exp( h0 + h1*log(tht) + h2*tht$\hat$2 + h3*elev + h4*cr) \\
R> dg.formula <- dg $\sim$ exp( d0 + d1*log(dbh) + d2*hg + d3*cr + d4*ba  ) \\
R> labels <- list( "height.growth", "diameter.growth" )\\
R> inst <- $\sim$ tht + dbh + elev + cr + ba\\
R> start.values <- c(h0=-0.5, h1=0.5, h2=-0.001, h3=0.0001, h4=0.08,\\
R+   d0=-0.5, d1=0.009, d2=0.25, d3=0.005, d4=-0.02 )\\
R> model <- list( hg.formula, dg.formula )\\
R> model.3sls <- nlsystemfit( "3SLS", model, start.values, data=ppine,\\
R+   eqnlabels=labels, inst=inst ) \\
R> summary( model.3sls ) \\
}

@@

>>>>

%       $Id$

@@

% \code{
% R> library( systemfit ) \\
% R> data( ppine ) \\
% R> hg.formula <- hg $\sim$ exp( h0 + h1*log(tht) + h2*tht$\hat$2 + h3*elev + h4*cr) \\
% R> dg.formula <- dg $\sim$ exp( d0 + d1*log(dbh) + d2*hg + d3*cr + d4*ba  ) \\
% R> labels <- list( "height.growth", "diameter.growth" )\\
% R> inst <- $\sim$ tht + dbh + elev + cr + ba\\
% R> start.values <- c(h0=-0.5, h1=0.5, h2=-0.001, h3=0.0001, h4=0.08,\\
% R+   d0=-0.5, d1=0.009, d2=0.25, d3=0.005, d4=-0.02 )\\
% R> model <- list( hg.formula, dg.formula )\\
% R> model.3sls <- nlsystemfit( "3SLS", model, start.values, data=ppine,\\
% R+   eqnlabels=labels, inst=inst ) \\
% R> summary( model.3sls ) \\
% }

@@

\section{CVS Revision Log}
\begin{verbatim}
$Log$
Revision 1.5  2004/11/16 05:31:19  hamannj
added cvs header and log section. to be removed when submitted.

\begin{verbatim}
